\documentclass{article} [12 pt]
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}

\begin{document}

\title{Sample Questions: For preliminary round}
\author{Prajit Adhikari}
\maketitle

\begin{enumerate}
    \item What is the average of first $105$ natural numbers?  \newline Ans: $53$
    \item What is the number of $4$ digit numbers divisible by $9$?\newline Ans: $1000$
    \item What is the remainder when $4$ divides $3^{39}+ 5^{86}$?\newline Ans: $0$
    \item What do we call the composite numbers that satisfy Fermat's Last theorem?\newline Ans: Carmichael numbers
    \item Find the number of non-negative integer solutions to $a+b+c+d+e+f=15$.\newline Ans: $20 \choose 5$
    \item What is the remainder when $2^8$ is divided by $15$?\newline Ans: $1$
    \item Is the cardinality of natural number set equal to that of rational number set?\newline Ans: Yes
    \item What is the value of $i^i$?(where $i$ is the imaginary number)\newline Ans: $e^{\frac{-\pi}{2}}$
    \item What is the first square other than $0,1 $ in Fibonacci series?\newline Ans: $144$
    \item What is the area of Hexagon with side length $s=6$?\newline Ans: $93.53$ sq. units
    \item What does the sum of degree of each vertices of an undirected graph results in?\newline $ 2 \times$ number of edges
    \item What is the degree of loop in a graph?\newline Ans: $2$
    \item What is the path called which visits each vertex exactly once from starting point to terminal point?\newline Ans: Hamitonian Path
    \item If dangerous fires are rare $(3\%)$ but smoke is fairly common $(20\%)$ due to barbecues, and $90\%$ of dangerous fires make smoke then what is the probability of dangerous fire when smoke?\newline Ans: $13.5 \%$
    \item The point of intersection of radical axis of three intersecting circles is known as:\newline Ans: Miquel point 
    \end{enumerate}


\section*{Some subjective problems:}
\begin{enumerate}
    \item Show that if a and b are positive integers, then
    $$\bigg(a+\frac{1}{2}\bigg)^n + \bigg(b+\frac{1}{2}\bigg)^n$$
is an integer for only finitely many positive integers $n$.
\item Solve the functional equation
$$f(xf(x)+f(y))=y+f(x)^2, x,y \in R$$
\item Prove that among any ten points located on a circle with diameter $5$, there exist at least two at a distance less than $2$ from each other.
\item Triangle $ABC$ has $BC=20.$ The incircle of the triangle evenly trisects the median $AD.$ If the area of the triangle is $m \sqrt{n}$ where $m$ and $n$ are integers and $n$ is not divisible by the square of a prime, find $m+n.$
\end{enumerate}


\end{document}