\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage [margin=0.5 in, top= 0.7 in, bottom=0.8in]{geometry}
\usepackage{amsfonts}


\begin{document}

\begin{enumerate}
    \item Sabita has 8 stamp books that each contain 42 pages. Each page in her books contains 6 stamps. Sabita decides to reorganize her stamp books such that each page contains 10 stamps. This will give her more space to collect stamps without having to buy new books. Under her new system, Sabita fills up 4 complete books, still with 42 pages per book. Her fifth book now contains 33 pages filled with 10 stamps per page and 1 last page with the remaining stamps. How many stamps are on that last page? Ans: 6
    \item If $a$ is a constant such that $9x^2 + 24x + a$ is the square of a binomial, then what is $a$? Ans: 16
    \item Kimberly borrows $1000$ dollars from Rupa, who charged interest of $5\%$ per month (which compounds monthly). What is the least integer number of months after which Kimberly will owe more than twice as much as she borrowed? Ans: 15
    \item At a particular school with 43 students, each student takes chemistry, biology, or both. The chemistry class is three times as large as the biology class, and 5 students are taking both classes. How many people are in the chemistry class? Ans: 36
    \item Camy made a list of every possible distinct five-digit positive integer that can be formed using each of the digits 1, 3, 4, 5 and 9 exactly once in each integer. What is the sum of the integers on Camy's list? Ans:5866608
    \item Suppose that $ABCD$ is a trapezoid in which $\overline{AD}|| \overline{BC}$. Given $\overline{AC}\perp\overline{CD}$, $\overline{AC}$ bisects angle $\angle BAD$, and $[ABCD]=42$, then compute area of $\triangle ACD$.Ans: 28
    \item Evaluate $\lfloor6.7\rfloor+\lfloor-6.7\rfloor$. Ans: -1
    \item A point $(x,y)$ is randomly selected such that $0 \le x \le 8$ and $0 \le y \le 4$. What is the probability that $x+y \le 4$? Express your answer as a common fraction. Ans: 1/4
    \item For what number $A$ does the equation $3Ax - 24 = 5x - 9 + x$ have no solutions for $x$? Ans: 2
    \item For how many integers $n$ is it true that $\sqrt{n} \le \sqrt{4n - 6} < \sqrt{2n + 5}$? Ans: 4
    \item Find the positive base $b$ in which the equation $13\cdot15=243$ is valid. ANs: 6
    \item If the second term of a geometric sequence of real numbers is $-2$ and the fifth term is $16,$ then what is the fourteenth term? Ans: -8192
    \item What is the least whole number that is divisible by 7, but leaves a remainder of 1 when divided by any integer 2 through 6? Ans: 301
    \item The tens digit of a two-digit number exceeds the units digit by 1. If the number is divided by the sum of its digits, the quotient is 6. What is the number? Ans: 54
    \item The sum of 49 consecutive integers is $7^5$. What is their median?
    Ans: 343
    \item 
\end{enumerate}

















\end{document}